Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
Discussion RQ2 done

\section{Discussion}
Our results have been valuable in exploring the motives behind API changes and the causes of API evolution. When Analysing these results, the following interesting topics came to light:

@@

\subsection{How do companies actively drive API evolution?}

@@

\subsection{RQ1.1}

@@

\smallskip \noindent
\textbf{One law does not apply}
Strong evidence was found which suggests that the law of Conservation of Organisational Stability does not apply to APIs.

This is interesting becaues it means one cannot assume that APIs are e-type systems and it cannot be compared to ``normal'' systems in some cases. 
\smallskip \noindent
\textbf{Feedback system  }
Something that is very important and might be overlooked in API development/evolution

>>>>

\newpage
\section{Discussion}
Our results have been valuable in exploring the motives behind API changes and the causes of API evolution. When Analysing these results, the following interesting topics came to light:

@@

\newpage
\subsection{Discussion RQ1}

@@

\newpage
\subsection{Discussion RQ1.1}

@@

\smallskip \noindent
\textbf{One law does not apply  }
Strong evidence was found which suggests that the law of Conservation of Organisational Stability does not apply to APIs. Our results not only show that the law is not true for APIs, but that the opposite of what the law states is true for APIs. This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}. The results from our study also showed that the reluctancy to change APIs causes the releases of new versions to be few and sporadic.

\smallskip \noindent
\textbf{The importance of a Feedback System  }
Especially interesting results were found in regards to the law of Feedback System. The importance of having a structured and developed feedback loop was stressed during the interview, and it was also expressed as one of the main points of improvement. This suggests that including feedback from more sources and making use of this feedback should be done more when developing an API.
